Towards open collaboration in biomedical and health research: A scoping review

### 2022-11-03 doc/protocol.Rmd
added initial files for searches

---
title: "Towards open collaboration in biomedical and health research: A scoping review"
shorttitle: "Scoping review of open collaboration"
date: "`r Sys.setlocale('LC_TIME', 'C'); format(Sys.time(), '%d\\\\. %B %Y')`"
author: 
  - name: Hannah Chatwin
    affiliation: 2
  - name: Mario Garcia
    affiliation: 3
  - name: Daniel Ibsen
    affiliation: 1
  - name: Luke W. Johnston
    affiliation: "1,2"
affiliation:
  - id: 1
    institution: Steno Diabetes Center Aarhus, Denmark
  - id: 2
    institution: Aarhus University, Denmark
   - id: 3
    institution: Copenhagen University, Denmark
output: prereg::prereg_pdf
---

@@

@@

    -   Documents published >5 years in the past (defined as before 2017-01-01) to capture
        current/most recent practices.

>>>>

---
title: "Towards open collaboration in biomedical and health research: A scoping review"
shorttitle: "Scoping review of open collaboration"
date: "`r Sys.setlocale('LC_TIME', 'C'); format(Sys.time(), '%d\\\\. %B %Y')`"
author: 
  - name: Hannah Chatwin
    affiliation: 2
  - name: Mario Garcia
    affiliation: 3
  - name: Daniel Ibsen
    affiliation: 1
  - name: Luke W. Johnston
    affiliation: "1,2"
affiliation:
  - id: 1
    institution: Steno Diabetes Center Aarhus, Denmark
  - id: 2
    institution: Aarhus University, Denmark
  - id: 3
    institution: Copenhagen University, Denmark
output: 
    prereg::prereg_pdf: default
    md_document: default
---

@@

**Registration link:** <https://doi.org/10.17605/OSF.IO/K9DR5>

@@

    -   Documents published \>5 years in the past (defined as before
        2017-01-01) to capture current/most recent practices.
